Multiproduct Batch Processing Time Maximization Problem

### 2023-06-27 (2023) Fraga et al.tex
updating paper

To test the developed model and analytical solution method, we created a solver in C++ and a solver in LINGO (both available at github.com). We tested the solvers developed for the benchmarks presented below.

@@

\begin{table}[h]
\begin{center}
\begin{footnotesize}
\begin{tabular}[c]{l r r r r}
problem & LINGO solver & time (s) & analytical method & time (s) \\
\cline {1-5} \\
MBPTMP 1 & & & 52 & 0 \\
MBPTMP 2 & & & 46 & 0 \\
MBPTMP 3 & & & 30 & 0 \\
RMBPTMP 20 & & & 100 & 0 \\
RMBPTMP 50 & & & 98 & 0\\
RMBPTMP 100 & & & 98 & 0\\
RMBPTMP 1,000 & & & 78 & 0\\
RMBPTMP 10,000 & & & 70 & 0 \\
\cline {1-5} \\
\end{tabular}
\label{tab:results}
\caption{Results obtained with the LINGO solver and the analytical method}
\end{footnotesize}
\end{center}
\end{table}

>>>>

To test the developed model and analytical solution method, we created a solver in C++ and a solver in LINGO (both available at github.com). The tests were performed on a notebook with an Intel i7 processor. We tested the solvers developed for the benchmarks presented below.

@@

\begin{table}[h]
\begin{center}
\begin{footnotesize}
\begin{tabular}[c]{l r r r r}
problem & LINGO solver & time (s) & analytical method & time (s) \\
\cline {1-5} \\
MBPTMP 1 & 55 & 0 & 55 & 0.001 \\
MBPTMP 2 & 48 & 0.06 & 48 & 0.001 \\
MBPTMP 3 & & & 30 & 0.001 \\
RMBPTMP 20 & & & 100 & 0.001 \\
RMBPTMP 50 & & & 98 & 0.001\\
RMBPTMP 100 & & & 98 & 0.002\\
RMBPTMP 1,000 & & & 78 & 0.002\\
RMBPTMP 10,000 & & & 70 & 0.006 \\
\cline {1-5} \\
\end{tabular}
\label{tab:results}
\caption{Results obtained with the LINGO solver and the analytical method}
\end{footnotesize}
\end{center}
\end{table}
